%-------------------------
% CV for Arsham Mikaeili Namini
% License : MIT
%------------------------

% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=1in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large Arsham Mikaeili Namini }\\[7pt] % Name
\textbf{Curriculum Vitae}\\[3pt] % CV
Montréal, Canada | \href{mailto:arsham.mikaeilinamini@mail.mcgill.ca}{arsham.mikaeilinamini@mail.mcgill.ca} | (438) 470-0724 \\
\href{https://scholar.google.ca/citations?hl=en&pli=1&user=zoWS71IAAAAJ}{Google Scholar} | \href{https://github.com/Arshammik}{GitHub} | \href{https://www.linkedin.com/in/arsham-mikaeili-namini-a891ba186/}{Linkedin} % Contact info
\end{center}

%------------------------

% Education Section
\section*{EDUCATION}

\noindent
\newline
\textbf{M.Sc. in Human Genetics} \\
2023 - 2026(Expected) \\ 
Department of Human Genetics, Faculty of Medicine and Health Science  \\
McGill University, Montréal, QC, Canada \\ 
\\
\noindent
\textbf{B.Sc. in Biology} \\
2019 - 2023 \\ 
Department of Animal Biology, Faculty of Biological Science\\
Kharazmi University, Tehran, Tehran Province, Iran \\ 
GPA : 3.75 / 4.00\\
\\
\noindent
\textbf{Diploma of Natural Sciences} \\
2014 - 2018 \\ 
Shahid Soltani 1 High School\\ 
National Organization for Development of Exceptional Talents, Karaj, Alborz Province, Iran \\ 
GPA : 4.00 / 4.00\\

%------------------------

% Employment Section
\section*{RESEARCH EXPERIENCE}
\noindent
\newline
\textbf{Research Assistant} \\
August 2023 - Present \\
Supervisors: \href{https://scholar.google.com/citations?user=7RluIhUAAAAJ&hl=en}{Hamed S. Najafabadi, Ph.D.},  \href{https://scholar.google.com/citations?user=nTabYNcAAAAJ}{Yasser Riazalhosseini, Ph.D.}\\
Department of Human Genetics \\
Faculty of Medicine and Health Science, Montréal, QC, Canada \\ 
Investigating alternative splicing mechanisms in different cancer types and establishing a statistical framework for mRNAs isoforms quantification using scRNA-Seq data. \\ 


\noindent
\textbf{Research Fellow} \\
June 2022 - June 2023 \\
Supervisor: \href{https://scholar.google.com/citations?user=o2NAtDIAAAAJ&hl=en}{Abolfazl Movafagh, Ph.D.}\\
Department of Medical Genetics \\
Shahid Beheshti University of Medical Sciences, Tehran, Tehran Province, Iran \\ 
An in-silico investigation on mRNAs and lncRNAs deregulation in metastatic small cell lung cancer and revealing potential biomarker for brain metastatic SCLC. \href{https://drive.google.com/file/d/1HORJcyF-bwOsYw6FeWyZysfa3_7bd7uB/view}{Project Details} \\ 



\noindent
\textbf{Research Assistant} \\
August 2021 - June 2023  \\
Supervisor: \href{https://scholar.google.com/citations?hl=en&user=TA6BGwcAAAAJ}{Youping Deng, Ph.D.} \\
Department of Quantitative Health Sciences \\
University of Hawaii at Mānoa, Honolulu, HI, USA \\ 
Tracking mutation patterns on a whole-genome scale of ~6 million COVID-19 samples and studied region-specific mutations to demonstrate the achievement rate of different vaccine types. \\

\noindent
\textbf{Teacher Assistant} \\
May 2022 - August 2022 \\
A meta-analysis project aimed nine different metastatic breast cancer cohorts.
Teaching an introduction to R programming and essential packages for NGS data analysis.\\

\noindent
\textbf{Lab Intern} \\
July 2021 - July 2021 \\
Department of Stem Cell Biology  \\
Royan Institute, Tehran, Tehran Province, Iran\\
A three-week internship focused on essential laboratory skills for research purposes, including MEF cell culture and cryobiology techniques. Histotechniuqe and slide preparation and female embryology surgery techniques. 

%------------------------

% Publications Section
\section*{PUBLICATIONS}
 
\subsection*{Peer Reviewed Articles}
\textbf{An in silico comparative transcriptome analysis identifying hub lncRNAs and mRNAs in brain metastatic small cell lung cancer (SCLC)} \\ 
\textbf{Arsham Mikaeili Namini}, Motahareh Jahangir, Maryam Mohsen, Ali Asghar Kolahi, Hossein Hassanian-Moghaddam, Zeinab Mazloumi, Marzieh Motallebi, Mojgan Sheikh- pour, Abolfazl Mobafagh*. Scientific Reports.  \href{https://www.nature.com/articles/s41598-022-22252-7}{10.1038/s41598-022-22252-7}\\
\\
\textbf{Comparative analysis of protein-protein interaction networks in metastatic breast cancer} \\ 
Hozhabri, Roxana Sadat Ghasemi Dehkohneh, Seyed Morteza Razavi, S. Mostafa Razavi, Fatemeh Salarian, Azade Rasoul, Jalil Azami, Melika Ghasemi Shiran, Zahra Kardan, Negar Farrokhzad, \textbf{Arsham Mikaeili Namini}, Ali Salari*. PLoS ONE. \href{https://doi.org/10.1371/journal.pone.0260584}{10.1371/journal.pone.0260584}

\subsection*{Pre Prints}
\textbf{The First Geographic Identification by Country of Sustainable Mutations of SARS-COV2 Sequence Samples: Worldwide Natural Selection Trends} \\
Mohammadamin Mahmanzar, Taleb Hoseini, Karim Rahimian, \textbf{Arsham Mikaeili Namini}, Shahrzad Ahangarzadeh, Reza Mahmanzar, Youping Deng*. BioRxiv. \href{https://doi.org/10.1101/2022.07.18.500565}{2022.07.18.500565/10.1101}

%------------------------

% Awards and Honors Section
\section*{AWARDS AND HONORS}

\noindent
\newline
\textbf{Grad Excellence Award} \\
2023 \\
McGill University, Montréal, QC, Canada \\
\\
\noindent
\textbf{ Exceptional Talent Award} \\
2022 \\
Kharazmi University, Tehran, Tehran Province, Iran \\
Qualified for every M.Sc. program in biological sciences field in any Iranian university.  \\


%------------------------

% Professional Skills Section 
\section*{PROFESSIONAL SKILLS}

\noindent
\newline
\textbf{Programming} \\
Advanced R and Python programming with a focus on developing genomics and transcriptomics computational tools. Familiar with Unix/Linux machines and bash scripting. Advanced user of git version control system. Familiar with web programming using javascripts frameworks (React and Vue) and HTML/CSS scripting.\\

\noindent
\textbf{Bioinformatic Tools} \\
Familiar with some of the widely used bioinformatic tools like BLAST, Oligo 7, SPSS, QUAST, MEME, SPAdes assembler, Bioedit, pyMOL, VMD, IGV, Cytoscape, and Galaxy.  \\

\noindent
\textbf{Wet Lab Skills} \\
DNA extraction, cDNA synthesis, PCR (regular and RT), primer design, gel electrophoresis (regular and 2D), gel documentation, CR-Seq, and DNA purification. \\

\noindent
\textbf{General Tools} \\
Adobe Illustrator, Figma, Adobe InDesign, Inkscape, Final Cut Pro, Endnote, Mendeley, Slack, Notion, and Overleaf.


%------------------------

% Professional Memberships Section 
\section*{CERTIFICATES}

\noindent
\newline
\textbf{Bioinformatics Specialization (7 Courses)} \\
University of California San Diego, San Diego, CA, USA\\ \href{https://www.coursera.org/account/accomplishments/specialization/EV4TMKLBTG63}{Validation}\\

\noindent
\textbf{Introduction to Genomic Technologies and Python for Genomic Data Science} \\
Johns Hopkins University, Baltimore, MD, USA\\
\href{https://www.coursera.org/account/accomplishments/records/R52ZVQVWLBUG}{Validation}, \href{https://www.coursera.org/account/accomplishments/records/83F8LA8HLETP}{Validation}\\

% End document
\end{document}
